Changelog

### 2021-05-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of a cache line instead of a cache set. While Flush+Reload targets a single cache line, it requires the attacker and victim to share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory, which may be a load of the sensitive information to the cache line.  In the next phase,
the attacker reloads the ``monitored memory''. The attacker's process read all data in the `monitored
memory''. If the time is relatively fast, it indicate that the data has been accessed by the victim program and the cache has loaded the data. 
On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.

>>>>

\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe memory accesses at the granularity of a cache line instead of a cache set. While Flush+Reload has a fine-grained granularity compared with Prime+Probe, it requires the attacker and victim to share some memory. It also has two stages. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory, which may be a load of the sensitive information to the cache line.  In the next phase,
the attacker reloads the ``monitored memory''. The attacker's process read all data in the `monitored
memory''. If the time is relatively fast, it indicate that the data has been accessed by the victim program and the cache has loaded the data. 
On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
